Study of the Empirical Distribution of Ties in Irrational Numbers

### 2020-11-08 Reports/JOURNAL - Confidence Regions/Chapters/Conclusions.tex
Sincronizanto

We present and evaluate a new method of building empirical confidence regions in the Entropy-Complexity plane for the analysis of white noise.
The following proposal consists of two stages:
(1)~the construction of empirical confidence regions obtained through the mapping of points in the latent space formed by the application of the principal components analysis under the reference points,
(2) ~ the application of a hypothesis test to measure the similarity of new sequences to the reference points.
Sequences of true random samples were used to calculate theses empirical regions.

>>>>

We present and evaluate a new method of building empirical confidence regions in the Entropy-Complexity plane for the analysis of white noise.
The following proposal consists of two stages:
(1)~the construction of empirical confidence regions obtained through the mapping of points in the latent space formed by the application of the principal components analysis under the reference points,
(2)~the application of a hypothesis test to measure the similarity of new sequences to the reference points.
Sequences of true random samples were used to calculate theses empirical regions.

### 2020-11-08 Reports/JOURNAL - Confidence Regions/Chapters/Introduction.tex
Sincronizanto

Although the boundaries of the $H\times C$ are well-defined, a complete characterization of its intrinsic topology is an open problem.
Several works have used deterministic and pseudorandom sequences aiming at understanding its properties.
\cite{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties} analyzed the logistic chaotic map and discuss the boundaries of the $H \times C$ plane.
\cite{De_Micco_2009} studied chaotic components in pseudorandom number generators.
\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos and noise.
\cite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.

>>>>

Although the boundaries of the $H\times C$ are well-defined, a complete characterization of its intrinsic topology is an open problem.
\citet{OrdinalPatternProbabilities} obtained properties of the sample entropy under zero mean Gaussian processes.
In particular, the joint distribution of points in this plane under typical types of time series would serve to build test statistics.

Several works have used deterministic and pseudorandom sequences aiming at understanding the properties of the points they produce in the $H\times C$ plane.
\cite{GeneralizedStatisticalComplexityMeasuresGeometricalAnalyticalProperties} analyzed the logistic chaotic map and discuss the boundaries of the $H \times C$ plane.
\cite{De_Micco_2009} studied chaotic components in pseudorandom number generators.
\cite{DistinguishingNoiseFromChaos}  tackled the often hard problem of distinguishing chaos from noise.
\cite{DistinguishingChaoticStochasticDynamicsTimeSeriesMultiscaleSymbolicApproach} used a multi-scale approach to analyze the interplay between chaotic and stochastic dynamics.

### 2020-11-08 Reports/Report - Data Imputation/Code/EmpiricalDistributionTies.Rmd
Sincronizanto

---
title: "Study of the Empirical Distribution of Ties in Irrational Numbers"
author: "Eduarda Chagas"
date: "Nov 7, 2020"
output: html_notebook
---

@@

>>>>

---
title: "Study of the Empirical Distribution of Ties in Irrational Numbers"
author: "Eduarda Chagas"
date: "Nov 7, 2020"

output: html_notebook
---

@@

We have produced to files with Mathematica: e.txt, pi.txt, and sqrt2.txt. They contain expansions of these irrational numbers with $100,000$ digits.

The exploratory data analysis consists of

1. Read the numbers, and for each number:
2. For each value of $D\in\{3,4,5,6\}$ (or embedding dimensions employed in the literature)
3. Compute the number of tied sequences
4. Return binary vectors with the position of the tied sequences
